MASCARA: coexpression analysis in data from designed experiments

### 2024-01-10 R/Paper_markdown.Rmd
renv_update

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, fig.pos = "H") #, root.dir=here()

if(!"renv" %in% installed.packages()[,1]){
  install.packages("renv")
}

renv::restore(prompt = FALSE)

@@

```{r, echo = FALSE, include=FALSE}
library(devtools)
library(ggplot2)
library(MetStaT)
library(gASCA)
library(patchwork)
library(readxl)
library(ggfortify)
library(ggrepel)
library(grid)
library(gridExtra)
library(tidyr)
library(tidyverse)
library(reshape2)
library(scales)
library(matrixStats)
library(DESeq2)
library(MASS)
library(glmnet)
library(doParallel)
library(MUVR)
library(pheatmap)
library(caret)
library(mixOmics)
library(cowplot)
library(reticulate)
library(biomformat)
library(MetStaT)
library(DiscriMiner)
library(viridis)
library(directlabels)
library(ggpmisc)
library(DescTools)
library(data.table)
library(plotly)
library(ggbreak)

@@

library(rhmmer)
REF2 <- as.data.frame(read_tblout("Rice_Annotation/HMM_ITAG_1.txt"))

>>>>

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, fig.pos = "H") #, root.dir=here()
# install.pacakges()

# if(!"renv" %in% installed.packages()[,1]){
#   install.packages("renv")
# }
# 
# renv::restore(prompt = FALSE)
# renv::snapshot()

# renv::dependencies()
# renv::status()

@@

```{r, echo = FALSE, include=FALSE}
library(devtools)
library(ggplot2)
library(MetStaT)
library(gASCA)
library(patchwork)
library(readxl)
library(ggfortify)
library(ggrepel)
library(grid)
library(gridExtra)
library(tidyr)
library(tidyverse)
library(reshape2)
library(scales)
library(matrixStats)
library(DESeq2)
library(MASS)
library(glmnet)
library(doParallel)
library(MUVR)
library(pheatmap)
library(caret)
library(mixOmics)
library(cowplot)
library(reticulate)
library(biomformat)
library(DiscriMiner)
library(viridis)
library(directlabels)
library(ggpmisc)
library(DescTools)
library(data.table)
library(plotly)
library(ggbreak)
library(rhmmer)
```

```{r}
# renv::snapshot()  #change this

@@

REF2 <- as.data.frame(read_tblout("Rice_Annotation/HMM_ITAG_1.txt"))
